Quantifying Directionality and Innovation Output in Sweden's Transition to a Forest-Based Bioeconomy

### 2024-09-12 notebooks/14-plots.qmd
rename experiments to notebooks

innovation_trends_plot
ggsave(here("results/figures/innovation_trends.pdf"), width = 7, height = 5)
```

@@

```{r}
batlow_discrete <- paletteer::paletteer_c("scico::batlowW", n = 5)
```

@@

ggsave(here("results/figures/vision_count.pdf"), vision_count_plot)
```

>>>>

innovation_trends_plot
ggsave(here("results/figures/innovation_trends.pdf"), width = 7, height = 5)
ggsave(here("results/figures/innovation_trends.svg"), width = 7, height = 5)
```

@@

```{r}
batlow_discrete <- paletteer::paletteer_c("scico::batlowW", n = 5)
batlow_discrete
```

@@

ggsave(here("results/figures/vision_count.pdf"), vision_count_plot)
ggsave(here("results/figures/vision_count.svg"), vision_count_plot)
```
